Figures

### 2019-11-01 figures/07_model-selection_40.Rmd
more file name typo fixes

re_brms        <- readRDS("../data/mcmc/re_brms.rds")
pred_key       <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
```

@@

```{r pre_tn_fe, out.width="3.45in", out.height="4in"}
# autoselect best tn model
re_names <- unlist(lapply(re_brms, function(x) 
  get_re_text(as.character(x$formula)[[1]])))[seq((length(re_brms)/2) + 1,
                                                  length(re_brms))]
best_tn <- loo_compare(
  lapply(seq((length(re_brms)/2) + 1, length(re_brms)), 
         function(x) re_brms[[x]]$loo))
best_tn <- which(re_names == row.names(best_tn)[1])

fit_tn         <- re_brms[[best_tn]] 
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

>>>>

re_brms        <- readRDS("../data/mcmc/re_brms_40.rds")
pred_key       <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
```

@@

```{r pre_tn_fe, out.width="3.45in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
# re_brms[[8]]$formula
# brms::bayes_R2(re_brms[[8]])

best_tn        <- 8 # 11 is best tn model with random effects
fit_tn         <- re_brms[[best_tn]] 
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
